Supporting Information: Demographic history and patterns of selection in maize during and since domestication

### 2015-11-13 supportingInfo.tex
updates

\jri{first figure should be below header}
\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=.85\textwidth]{FigsAndFiles/plotDiversity_TvM_Folded2_Significance_tga1Supp_June.png} \\
    \end{center}
\caption{Diversity surrounding the causitive substitution at the \emph{tga1} locus.  \label{sFig:tga1}}
\end{figure}
\clearpage

\begin{figure}
  \begin{center}
    \includegraphics[width=.85\textwidth]{FigsAndFiles/BKN_TIL_msmc.pdf} \\
    \end{center}
\caption{\jri{need MSMC caption, remove gray background, fix axis labels and plot legend.} \label{sFig:msmc}}
\end{figure}
\clearpage

>>>>

\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=.85\textwidth]{FigsAndFiles/plotDiversity_TvM_Folded2_Significance_tga1Supp_June.png} \\
    \end{center}
\caption{Diversity surrounding the causitive substitution at the \emph{tga1} locus.  \label{sFig:tga1}}
\end{figure}
\clearpage

\begin{figure}
  \begin{center}
    \includegraphics[width=.85\textwidth]{FigsAndFiles/TIL_BKN_bootstrapping_msmc.pdf}
    \end{center}
\caption{Population size estimates from six haplotypes (six highly inbred lines) from both maize and teosinte revealed by MSMC analyses. \label{sFig:msmc}}
\end{figure}
\clearpage
